%-------------------------
% Resume in Latex
% Author : Daniel Strohfeldt
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Daniel Strohfeldt -- Firmware Engineer}} & Email : \href{mailto:daniel.strohfeldt@gmail.com}{daniel.strohfeldt@gmail.com}\\
 Mobile : +1-608-316-5610 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wisconsin - Milwaukee}{Milwaukee, WI}
      {Bachelor of Science in Computer Engineering;  GPA: 3.5}{2012 -- 2017}
    \resumeItemListStart
      \resumeItem{Vice President of IEEE}{Managed sales and creation of lab kits for all Electrical Engineering courses. Held seminars for student enrichment. Managed lab equipment for use by students.}
    \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Tesla, INC.}{Palo Alto, CA}
      {Firmware Engineer - Intern}{Jan 2017 - Present}
      \resumeItemListStart
        \resumeItem{Software in the Loop - Body Controls Firmware}
          {A tool used to validate and verify new firmware features and test regressions on existing features, without existing hardware.
          \begin{itemize}
          \item One of three core developers of the Body Controls team's software in the loop platform. Which is used daily by 7-9 firmware validation engineers and 20 - 25 firmware engineers reap the benefits of.
          \item Developed firmware drivers and implemented front end for non-existent features and maintained existing features of the platform.
          \item In my first 2 weeks, I implemented a new algorithm for creating viewable IO traces from the firmware, resulting in 20x speedup.
          \end{itemize}}
        \resumeItem{Validation - Body Controls Firmware}
          {Validation and verification of new firmware features.
          \begin{itemize}
          	\item Tested Model S and X E-Fuse self test behaviors without existing hardware. Created regression test suite for Model S and X E-Fuse manufacturing self test, resulting in saved 12 volt batteries.
            \item Developed tests for manufacturing ride height calibrations and installations of both air suspension and coil suspension for Model 3.
            \item Tested new features of the Model 3 steering column adjustments which couldn't be verified using Hardware.
          \end{itemize}}
      \resumeItemListEnd

    \resumeSubheading
      {University of Wisconsin - Milwaukee}{Milwaukee, WI}
      {Research Assistant}{Aug 2015 - Jan 2017}
      \resumeItemListStart
        \resumeItem{Non-Destructive Evaluation - Magnetic Flux Leakage}
          {Robotics project funded by the United States Federal Highway Administration.
          \begin{itemize}
          	\item Designed and fabricated sensor payload, used to detect and track magnetic flux leakage in 3 axes.
            \item Developed real-time data visualization software for field scans of reinforced concrete structures.
            \item Developed post-processing software to isolate areas of structural defect, in order to identify locations at which the structure should be reinforced.
            \item Wrote reports for the USFHWA, to show progress and relay technical information in a way that the layman could understand. 
            \end{itemize}}
        \resumeItemListEnd

    \resumeSubheading
      {EDCS Power}{Mequon, WI}
      {Electrical Engineer - Intern}{May 1015 - Aug 2015}
      \resumeItemListStart
        \resumeItem{Data Acquisition and Control Algorithm}
          {Start-Up company focused on creating high efficiency uninterruptible power supplies for servers. 
          \begin{itemize}
          	\item Developed sensing circuitry for 100 kW AC to DC power supply.
            \item Developed technology for syncing function generators in order to create 3 phase waveforms.
            \item Worked on gate drive circuitry. Tested Silicon Carbide mosfets to determine characteristics unknown to the data sheet.
            \item Worked with Microsemi FPGA to implement control algorithm used to switch the three phase 380V AC power to +/- 190V DC power.
          \end{itemize}}
        \resumeItemListEnd

    \resumeSubheading
      {City of Madison}{Madison, WI}
      {Civil Engineer - Intern}{May 2014 - Sept 2014}
      \resumeItemListStart
        \resumeItem{East Johnson Street}
          {10 million dollar road construction project in Madison, WI.
          \begin{itemize}
          	\item Coordinated with multiple engineering firms and construction companies, to effectively meet project deadlines.
            \item Oversaw construction crews to ensure project plan was followed and city building codes were met.
            \item Recorded accurate measurements and data used to determine payment for contracted construction companies.
          \end{itemize}
        }
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

